---
title: "Project steps"
output: html_document
author: 
date: 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
article:
<https://peerj.com/articles/9444/?fbclid=IwAR12-9ZUjajX1RTVnOxq0ucKSzzEapbWVwP32luc02H9oAvuZdYFpquKrlA#material-and-methods>

### 1. github

#### create the github repository on R:
in Terminal: paste the github link for Project repository
write "git clone"
enter

#### github to give access to Elizabeth on github:
settings>manage access> collaborators >invite a collaborator

#### to update the work on github
tick commit on the git window in Rstudio, select all, click push


## Data processing 


### 1- In your Hypothesis 1, you should explain why by random you expect H0 to be lower or equal instead of only equal. The same issue occurs with Hypothesis 2. I do not know why before the experiment do you expect to have differences between the two species.

**Hypothesis 1**
 
H0: Frond and root growth of L. minor will be equal in treatments involving LLE of Alnus glutinosa to in treatments involving LLE Acer negundo.

H1: Frond and root growth of L. minor will be different in treatments involving LLE of Alnus glutinosa from in treatments involving LLE Acer negundo. 

**Hypothesis 2**

H0: Accumulation of Cu, concentration of hydrogen peroxide and lipid peroxidation expressed as MDA concentration in L. minor will be equal in treatments involving LLE of Alnus glutinosa than in treatments involving LLE Acer negundo.

H1: Accumulation of Cu, concentration of hydrogen peroxide and lipid peroxidation expressed as MDA concentration in L. minor will be different in treatments involving LLE of Alnus glutinosa than in treatments involving LLE Acer negundo.

### 2- The article and the data are interesting, but data are messy, separated in several tables and not well explained with Metadata. Therefore, your first step should be to import all the data in one or more data frames, carefully from links and explain what each variable means. For this you can use the article.

 The independent variables for GrowthRAtes are the following treatments: 
1. Control
2. 100 µM CuSO4 (Cu)
3. Cu + AG leaf litter extracts (LLE) of 10 mg/L DOC (Cu+10-DOC_AG)
4. Cu + AG leaf litter extracts (LLE) of 100 mg/L DOC (Cu+100-DOC_AG)
5. (100-DOC_AG)
6. Cu + AN LLE of 10 mg/L DOC (Cu+10-DOC_AN)
7. Cu + AN LLE of 100 mg/L DOC (Cu+100-DOC_AN)
8. (100-DOC_AN)


# Data for growth rates of Frond and Roots in L.minor under 8 treatments. 
library(readxl)
RawData_GrowthRates <- read_excel("Raw_Data_Fig_1_Growth_rates (5).xlsx", 
                                                   range = "K13:M77")

#The independent variables for Cu accumulation are the following treatments:
1. Control
2. (Cu)
3. (Cu+10-DOC_AG) or (Cu+10-DOC_AN)
4. (Cu+100-DOC_AG) or (Cu+100-DOC_AN)

#Data for Cu accumulation in L.minor treated by Cu, and combinations of Cu and LLE from A. glutinosa.

```{r}
library(readxl)
RawData_Cu1 <- read_excel("Raw_Data_Fig_2_Cu_conc.xlsx", 
                                     range = "B10:I26")
```


#Data for Cu accumulation in L.minor treated by Cu, and combinations of Cu and LLE from A. negundo.
library(readxl)
RawData_Cu2 <- read_excel("Raw_Data_Fig_2_Cu_conc.xlsx", 
                                     sheet = "Cu_µg_gFW_AN", range = "B10:I26")

#The independent variables for Cu accumulation are the following treatments:
1. Control
2. (Cu)
3. (Cu+10-DOC_AG) or (Cu+10-DOC_AN)
4. (Cu+100-DOC_AG) or (Cu+100-DOC_AN)
5. (100-DOC_AG) or (100-DOC_AN)

#Concentration of hydrogen peroxide in L. minor treated by Cu, A. glutinosa LLE and Cu + A. glutinosa LLE.
library(readxl)
RawData_H2O2_1 <- read_excel("Raw_Data_Fig_3_H2O2_conc.xlsx", 
                                       range = "B10:I50")
#Concentration of hydrogen peroxide in L. minor treated by Cu, A. negundo LLE and Cu + A. negundo LLE.
library(readxl)
RawData_H2O2_2 <- read_excel("Raw_Data_Fig_3_H2O2_conc.xlsx", 
                                       sheet = "H2O2_AN", range = "B10:I50")

#The independent variables for Lipid Perodixation are the following treatments:
1. Control
2. (Cu)
3. (Cu+10-DOC_AG) or (Cu+10-DOC_AN)
4. (Cu+100-DOC_AG) or (Cu+100-DOC_AN)
5. (100-DOC_AG) or (100-DOC_AN)

#Lipid peroxidation expressed as MDA concentration in L. minor treated by Cu, A. glutinosa LLE and Cu + A. glutinosa LLE.
library(readxl)
RawData_Lipid1 <- read_excel("Raw_Data_Fig_4_Lipid_peroxidation.xlsx", 
                                                range = "B10:I50")
#Lipid peroxidation expressed as MDA concentration in L. minor treated by Cu, A. negundo LLE and Cu + A. negundo LLE.
library(readxl)
RawData_Lipid2 <- read_excel("Raw_Data_Fig_4_Lipid_peroxidation.xlsx", 
                                                sheet = "MDA_AN", range = "B10:I50")



### 3- For the treatment variables, I would separate the treatment variable in two or three different treatment variables. The first one for Cu present or absent and the second one for the Organic Matter concentration from each species.

#Try different approaches and choose the one you think represent better the results.

 

### 4- I would not start directly with a Manova. I advise you first to plot your results and do direct one or two way anovas for each dependent variable (as they do in the article). After knowing this results they might be better modeled with a manova.

 

### 5- For Post-Hoc comparisons use the Tukey test and compare the results with the used Dunne test. ¿Why do they use this test instead of the most usual?.

 

### 6- With all the chemical activity data, after doing the direct analysis, you should put all those data together and try a multivariate analysis. A good tutorial for this is: http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/118-principal-component-analysis-in-r-prcomp-vs-princomp/

### For this analysis it probably is more work to put the data in the right shape that doing the analyses. From this analysis you can see how the chemical activity groups and if this grouping can be explained by the treatments.

 


