---
title: "Results"
author: "Carpentero, Da Cruz Albertazzi, Gonzalez--Dehennault, Jyakhwa"
date: "2020.12.15"
output: html_document
---

```{r echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 

```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.path = "Results/", #to save the figures
                      dev = "png",#save in png
                      dpi = 100)
```

```{r echo=FALSE}
#install.packages("agricolae")
#install.packages("readxl")
```
 
## Cu concentration
#
### **For _Acer negundo_ leaf extracts**



```{r echo=FALSE, include=FALSE}
library(readxl)
Cu_AG <- read_excel("0.Data/Raw_Data_Fig_2_Cu_conc.xlsx", 
                    range = "B10:i26", col_names = TRUE)
Cu_AN <- read_excel("0.Data/Raw_Data_Fig_2_Cu_conc.xlsx", 
                    sheet = "Cu_µg_gFW_AN", range = "B10:I26")


colnames(Cu_AG)[colnames(Cu_AG) == "Cu_µg_gFW_AG"] <- "Trt"
colnames(Cu_AN)[colnames(Cu_AN) == "Cu_µg_gFW_AN"] <- "Trt"


AN <- "AN"
AG <- "AG"
Cu_AN <- dplyr::mutate(Cu_AN, Tree_sp = AN)

Cu_AG <- dplyr::mutate(Cu_AG, Tree_sp = AG)



library(tidyr)
Cu <- dplyr::bind_rows(Cu_AG, Cu_AN)


colnames(Cu)[colnames(Cu) == "48h"] <- "Fourtyeight"
colnames(Cu)[colnames(Cu) == "0.75h"] <- "Zero.seventyfive"
colnames(Cu)[colnames(Cu) == "1.5h"] <- "One.five"
colnames(Cu)[colnames(Cu) == "3h"] <- "Three"
colnames(Cu)[colnames(Cu) == "6h"] <- "Six"
colnames(Cu)[colnames(Cu) == "12h"] <- "Twelve"
colnames(Cu)[colnames(Cu) == "24h"] <- "Twentyfour"
colnames(Cu_AN)[colnames(Cu_AN) == "48h"] <- "Fourtyeight"

library(dplyr)
Cu2 <- Cu %>% 
  group_by(Trt, Tree_sp) %>% 
  summarise(mean = mean(Fourtyeight))

colnames(Cu2)[colnames(Cu2) == "mean"] <- "meanFourtyeight"

```


#### 1.Testing the normality of the data
```{r, fig.cap = "Figure 1. QQ plot and linear model.This gives us a vision of whether the data follows a linear model or not"}

#Fourtyeight in the name
# Build the linear model
model_Cu_an  <- lm(Fourtyeight~Trt, data = Cu_AN)

# Create a QQ plot of residuals
qqnorm(model_Cu_an[["residuals"]], main = "QQ plot for model_Cu_an")
qqline(model_Cu_an[["residuals"]])

```



#### 2.Kruskall-Wallis groups and plot

```{r, warning=FALSE, fig.cap = "Figure 2.Copper concentration in Lemna minor 48 hours after applying treatments with Copper and _Acer negundo_ extracts"}
library(agricolae)
Krus_Cu_an<- agricolae::kruskal(Cu_AN$Fourtyeight, Cu_AN$Trt)
Krus_Cu_an
# we get letters for the groups: the four treatments have each a different 
#group (d,a,c,b)

#add the group letters to the boxplot
boxplot(Fourtyeight~Trt, data = Cu_AN,
        ylim = c(0,460),
        ylab="Cu concentration in µg g^(−1)FW",
        xlab="Treatments", 
    main = "Copper concentration in Lemna minor 48h after treatments 
    with Copper and Acer negundo extracts",
   border=c("2","3","6","7","darkgreen"))
legend(x = 0.4, y = 330, 
       legend = c("Legend:","1: Control", "2: Cu", "3: Cu+10-DOC_AN ", 
                  "4: Cu+100-DOC_AN "), 
       cex = 0.8)
text(x=(1:4) , c("d","a","c","b"), pos = 3, y = c(30,415,210,390))

```
#
### **For _Alnus glutinosa_ leaf extracts**


#### 1.Testing the normality of the data

```{r, fig.cap = "Figure 3. QQ plot and linear model.This gives us a vision of whether the data follows a linear model or not"}

#Fourtyeight in the name
# Build the linear model
colnames(Cu_AG)[colnames(Cu_AG) == "48h"] <- "Fourtyeight"
model_Cu_ag  <- lm(Fourtyeight~Trt, data = Cu_AG)

# Create a QQ plot of residuals
qqnorm(model_Cu_ag[["residuals"]], main = "QQ plot for model_Cu_ag")
qqline(model_Cu_ag[["residuals"]])

```
#

#### 2.Kruskall-Wallis groups and plot


```{r, fig.cap= "Figure 4. Copper concentration in Lemna minor 48 hours after applying treatments with Copper and _Acer glutinosa_ extracts" }

#We use Kruskal wallis test because the data is not normal.
#Test for differences between treatments using agricolae::kruskal test.
#install.packages("agricolae")
library(agricolae)
Krus_Cu_ag<- agricolae::kruskal(Cu_AG$Fourtyeight, Cu_AG$Trt)
Krus_Cu_ag

boxplot(Fourtyeight~Trt, data = Cu_AG,
        ylim = c(0,460),
        ylab="Cu concentration in µg g^(−1)FW", xlab="Treatments", 
        main = "Copper concentration in Lemna minor 48h after treatments 
        with Copper and Alnus glutinosa extracts",
border=c("2","3","6","7","darkgreen"))
legend(x = 0.4, y = 330, 
       legend = c("Legend:","1: Control", "2: Cu", "3: Cu+10-DOC_AG ", 
                  "4: Cu+100-DOC_AG "), 
       cex = 0.8)
text(x=(1:4) , c("c","a","b","a"), pos = 3, y = c(30,410,260,420))
```
#
## Frond Growth Rate (FGR) and Root Growth Rate (RGR)

```{r echo=FALSE, include=FALSE}
library(readxl)
GR <- read_excel("0.Data/Raw_Data_Fig_1_Growth_rates.xlsx", 
                 range = "K13:M77")
library(dplyr)
GR1 <- GR %>% 
  group_by(Variant) %>% 
  summarise(meanF = mean(FrondGR), meanR = mean(RootGR))

#Subset of 1,2, 3, 4 and 5 treatments.
GR2 <- subset(GR, Variant == 1 | Variant == 2 | Variant == 3 | Variant == 4| Variant == 5)
```

#

### **For _Acer negundo_ leaf extracts**
#
### Frond Growth Rate

#### 1.Testing the normality of the data
```{r echo=FALSE}
#Subset of 1,2, 6, 7 and 8 treatments.
GR3 <- subset(GR, Variant == 1 | Variant == 2 | Variant == 6 | Variant == 7
              | Variant == 8)
```


```{r,fig.cap= "Figure 5. QQ plot and linear model"}
# Build the linear model
model3  <- lm(FrondGR~Variant, data = GR3)

# Create a QQ plot of residuals
qqnorm(model3[["residuals"]], main = "QQ plot for model")
qqline(model3[["residuals"]])

```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 6. Effect of Copper and _Acer negundo_ extract on Root Growth rate along 7 days"}
KrusFG3 <- agricolae::kruskal(GR3$FrondGR, GR3$Variant)
KrusFG3

boxplot(FrondGR~Variant, data = GR3,
        ylim= c(-0.4,0.3),
        ylab="Frond Growth rate (mm d^-1)", xlab="Treatments", 
        main = "Effect of Cu and AN on Frond Growth rate"
        ,border=c("2","3","6","7","darkgreen"))
legend("topright", legend=c("1: Control", "2: Cu", "6: Cu+10-DOC_AN ", 
                            "7: Cu+100-DOC_AN ", "8: 100-DOC_AN"), cex = 0.8,
       bty = "n", inset=c(0.03,0.7))
text(x=(1:5),y=c(0.23, -0.2, 0.04, 0.02, 0.22) , c("a","e","c","d","b"))
```

#
### Root Growth Rate
#### 1.Testing the normality of the data

```{r,fig.cap= "Figure 7. QQ plot and linear model"}
# Build the linear model
model4  <- lm(RootGR~Variant, data = GR3)

# Create a QQ plot of residuals
qqnorm(model4[["residuals"]], main = "QQ plot for model")
qqline(model4[["residuals"]])
```
#
#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 8. Effect of Copper and _Acer negundo_ extract on Root Growth rate along 7 days"}
KrusRG4 <- agricolae::kruskal(GR3$RootGR, GR3$Variant)
KrusRG4

boxplot(RootGR~Variant, data = GR3,
        ylim= c(0,0.9),
        ylab="Root Growth rate (mm d^-1)", xlab="Treatments", 
        main = "Effect of Cu and AN on Root Growth rate"
        ,border=c("2","3","6","7","darkgreen"))
legend("topright", legend=c("1: Control", "2: Cu", "6: Cu+10-DOC_AN ", 
                            "7: Cu+100-DOC_AN ", "8: 100-DOC_AN"), cex = 0.8,
       bty = "n", inset=c(0.03,0.03))
text(x=(1:5),y=c(0.82, 0.04, 0.15, 0.44, 0.57) , c("a","e","d","c","b"))
```
#
### **For _Acer glutinosa_ leaf extracts**
#
### Frond Growth Rate 

#### 1.Testing the normality of the data
```{r, fig.cap = "Figure 9. QQ plot and linear model"}

# Build the linear model
model  <- lm(FrondGR~Variant, data = GR2)

# Create a QQ plot of residuals
qqnorm(model[["residuals"]], main = "QQ plot for model")
qqline(model[["residuals"]])

```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 10. Effect of Copper and _Acer glutinosa_ extract on Frond Growth rate along 7 days"}
library(agricolae)

KrusFG <- agricolae::kruskal(GR2$FrondGR, GR2$Variant)
KrusFG

boxplot(FrondGR~Variant, data = GR2,
        ylim= c(-0.4,0.3),
        ylab="Frond Growth rate (mm d^-1)", xlab="Treatments", 
        main = "Effect of Cu and AG on Frond Growth rate"
        ,border=c("2","3","4","5","8"))
legend("topright", legend=c("1: Control", "2: Cu", "3: Cu+10-DOC_AG ", 
                            "4: Cu+100-DOC_AG ", "5: 100-DOC_AG"), cex = 0.8,
       bty = "n", inset=c(0.03,0.7))
text(x=(1:5),y=c(0.23, -0.2, 0.05, 0.09, 0.16) , c("a","e", "d","c","b"))
```
#
### Root Growth Rate
#### 1.Testing the normality of the data

```{r,fig.cap= "Figure 11. QQ plot and linear model"}
# Build the linear model
model2  <- lm(RootGR~Variant, data = GR2)

# Create a QQ plot of residuals
qqnorm(model2[["residuals"]], main = "QQ plot for model")
qqline(model2[["residuals"]])
```

#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 12. Effect of Copper and _Acer glutinosa_ extract on Root Growth rate along 7 days"}
library(agricolae)
KrusRG <- agricolae::kruskal(GR2$RootGR, GR2$Variant)
KrusRG

boxplot(RootGR~Variant, data = GR2,
        ylim= c(0,0.9),
        ylab="Root Growth rate (mm d^-1)", xlab="Treatments", 
        main = "Effect of Cu and AG on Root Growth rate"
        ,border=c("2","3","4","5","8"))
legend("topright", legend=c("1: Control", "2: Cu", "3: Cu+10-DOC_AG ", 
                            "4: Cu+100-DOC_AG ", "5: 100-DOC_AG"), cex = 0.8,
       bty = "n", inset=c(0.03,0.03))
text(x=(1:5),y=c(0.82, 0.05, 0.05, 0.22, 0.43) , c("a","d","d","c","b"))

```
#
### **For _Acer glutinosa_ and _Acer negundo_ leaf extracts**
#
### Frond Growth Rate 
```{r, echo=FALSE}
#Subset of 1,2, 3, 4, 6 and 7 treatments.
GR5 <- subset(GR, Variant == 1 | Variant == 2 | Variant == 3 | Variant == 4| Variant == 6| Variant == 7)

```


#### 1.Testing the normality of the data
```{r, fig.cap = "Figure 13. QQ plot and linear model"}

# Build the linear model
model7  <- lm(FrondGR~Variant, data = GR5)

# Create a QQ plot of residuals
qqnorm(model7[["residuals"]], main = "QQ plot for model")
qqline(model7[["residuals"]])

```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 14. Effect of Copper, _Acer glutinosa_ and _Acer negundo_ extracts on Frond Growth rate of Lenma Minor along 7 days."}
KrusFG7 <- agricolae::kruskal(GR5$FrondGR, GR5$Variant)
KrusFG7

boxplot(FrondGR~Variant, data = GR5,
        ylim= c(-0.4,0.3),
        ylab="Frond Growth rate (mm d^-1)", xlab="Treatments", 
        main = "Effect of AG and AN in the presence 
   of Cu on Frond Growth rate"
        ,border=c(2:7))
legend("topright", legend=c("1: Control", "2: Cu", "3: Cu+10-DOC_AG", 
                            "4: Cu+100-DOC_AG", "6: Cu+10-DOC_AN", "7: Cu+100-DOC_AN"), cex = 0.8,
       bty = "n", inset=c(0.03,0.03))
text(x=(1:6),y=c(0.22, -0.2, 0.04, 0.09, 0.05, 0.02) , c("a","e","d","b","c","d"))


```
#
### Root Growth Rate
#### 1.Testing the normality of the data

```{r,fig.cap= "Figure 15. QQ plot and linear model"}
# Build the linear model
model8  <- lm(RootGR~Variant, data = GR5)

# Create a QQ plot of residuals
qqnorm(model8[["residuals"]], main = "QQ plot for model")
qqline(model8[["residuals"]])

```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 16. Effect of Copper, _Acer glutinosa_ and _Acer negundo_ extracts on Root Growth rate of Lenma Minor along 7 days."}
KrusRG8 <- agricolae::kruskal(GR5$RootGR, GR5$Variant)
KrusRG8

boxplot(RootGR~Variant, data = GR5,
        ylim= c(0,0.9),
        ylab="Root Growth rate (mm d^-1)", xlab="Treatments", 
        main = "Effect of AG and AN in the presence 
        of Cu on Root Growth rate"
        ,border=c(2:7))
legend("topright", legend=c("1: Control", "2: Cu", "3: Cu+10-DOC_AG", 
                            "4: Cu+100-DOC_AG", "6: Cu+10-DOC_AN", "7: Cu+100-DOC_AN"), cex = 0.8,
       bty = "n", inset=c(0.03,0.03))
text(x=(1:6),y=c(0.82, 0.04, 0.04, 0.22, 0.15, 0.43) , 
     c("a","e","e","c","d","b"))


```
#
## H2O2 content

```{r echo=FALSE}
AG_H2O2 <- read_excel("0.Data/Raw_Data_Fig_3_H2O2_conc.xlsx", 
                      sheet = "H2O2_AG", range = "B10:I50")
AN_H2O2 <- read_excel("0.Data/Raw_Data_Fig_3_H2O2_conc.xlsx", 
                      sheet = "H2O2_AN", range = "B10:I50")
# Change colname of one column so we give the same name to AG_H2O2 and AN_H2O2 
#in both tables
colnames(AG_H2O2)[colnames(AG_H2O2) == "H2O2_AG"] <- "Trt"
colnames(AN_H2O2)[colnames(AN_H2O2) == "H2O2_AN"] <- "Trt"
#Trt is for the Treatment

#install.packages("tidyr")
AN_H2O2 <- dplyr::mutate(AN_H2O2, Tree_sp = AG)
AG_H2O2 <- dplyr::mutate(AG_H2O2, Tree_sp = AN)
H2O2 <- dplyr::bind_rows(AG_H2O2, AN_H2O2)
#we have table with the species and only one column of Trt(!!!!)

#rename the column 48h as Fourtyeight because having a number in the name 
# gives error message
colnames(H2O2)[colnames(H2O2) == "48h"] <- "Fourtyeight"
```
#
### **For _Acer negundo_ leaf extracts**


#### 1.Testing the normality of the data
```{r, fig.cap = "Figure 17. QQ plot and linear model."}

# Build the linear model
colnames(AN_H2O2)[colnames(AN_H2O2) == "48h"] <- "Fourtyeight"
model_AN_H2O2  <- lm(Fourtyeight~Trt, data = AN_H2O2)

# Create a QQ plot of residuals
qqnorm(model_AN_H2O2[["residuals"]], main = "QQ plot for model_AN_H2O2")
qqline(model_AN_H2O2[["residuals"]])
```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 18. H2O2 content in Lemna minor after being exposed to tretaments with Copper and _Acer negundo_ extracts."}
Krus_AN_H2O2<- agricolae::kruskal(AN_H2O2$Fourtyeight, AN_H2O2$Trt)
Krus_AN_H2O2
# we get letters for the groups: there are 3 different groups (a,b,c)

#add the group letters to the boxplot
boxplot(Fourtyeight~Trt, data = AN_H2O2,
        ylim = c(0,300),
        ylab="H2O2 content (% of the control)",
        xlab="Treatments", 
        main = "H2O2 content in Lemna minor after treatments with Copper 
  and Acer negundo extracts",
        border=c("2","3","6","7","darkgreen"))
legend(x = 0.4, y = 305, legend = c("Legend:"
                                      ,"1: Control", "2: Cu", "3: Cu+10-DOC_AN ", 
                                 "4: Cu+100-DOC_AN ", "5: 100-DOC_AN"), 
       cex = 0.8)
text( c("c","b","b","a", "c"),x=(1:5) ,y = c(140,170,170,220,130))


```
#
### **For _Acer glutinosa_ leaf extracts**


#### 1.Testing the normality of the data
```{r, fig.cap = "Figure 19. QQ plot and linear model."}

colnames(AG_H2O2)[colnames(AG_H2O2) == "48h"] <- "Fourtyeight"
# Build the linear model
model_AG_H2O2  <- lm(Fourtyeight~Trt, data = AG_H2O2)

# Create a QQ plot of residuals
qqnorm(model_AG_H2O2[["residuals"]], main = "QQ plot for model_AG_H2O2")
qqline(model_AG_H2O2[["residuals"]])
```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 20. H2O2 content in Lemna minor after being exposed to tretaments with Copper and _Acer glutinosa_ extracts."}
Krus_AG_H2O2<- agricolae::kruskal(AG_H2O2$Fourtyeight, AN_H2O2$Trt)
Krus_AG_H2O2
# we get letters for the groups: there are 4 different groups (a,b,c,d)

#add the group letters to the boxplot
boxplot(Fourtyeight~Trt, data = AG_H2O2,
        ylim = c(0,300),
        ylab="H2O2 content (% of the control)",
        xlab="Treatments", 
        main = "H2O2 content in Lemna minor after treatments with Copper 
  and Alnus glutinosa extracts",
        border=c("2","3","6","7","darkgreen"))
legend(x = 0.4, y = 305, legend = c("Legend:"
                                    ,"1: Control", "2: Cu", "3: Cu+10-AG ", 
                                    "4: Cu+100-DOC_AG ", "5: 100-DOC_AG"), 
       cex = 0.8)
text( c("c","b","b","a", "d"),x=(1:5) ,y = c(130,170,170,190,110))



```

#
## Lipid peroxidation

```{r echo=FALSE}
AG_Lipid <- read_excel("0.Data/Raw_Data_Fig_4_Lipid_peroxidation.xlsx", 
                       sheet = "MDA_AG", range = "B10:I50")

AN_Lipid <- read_excel("0.Data/Raw_Data_Fig_4_Lipid_peroxidation.xlsx", 
                       sheet = "MDA_AN", range = "B10:I50")
# Change colname of one column so we give the same name to Lipid_AG and 
#Lipid_AN in both tables
colnames(AG_Lipid)[colnames(AG_Lipid) == "MDA_AG"] <- "Trt"
colnames(AN_Lipid)[colnames(AN_Lipid) == "MDA_AN"] <- "Trt"
```
#
### **For _Acer negundo_ leaf extracts**


#### 1.Testing the normality of the data
```{r, fig.cap = "Figure 21. QQ plot and linear model."}

colnames(AN_Lipid)[colnames(AN_Lipid) == "48h"] <- "Fourtyeight"# Build the linear model
model_AN_Lipid  <- lm(Fourtyeight~Trt, data = AN_Lipid)

# Create a QQ plot of residuals
qqnorm(model_AN_Lipid[["residuals"]], main = "QQ plot for model_AN_Lipid")
qqline(model_AN_Lipid[["residuals"]])
```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 22.Lipid peroxidation expressed as MDA concentration in Lemna minor after treatments with Copper and _Acer negundo_ extracts."}
Krus_AN_Lipid<- agricolae::kruskal(AN_Lipid$Fourtyeight, AN_Lipid$Trt)
Krus_AN_Lipid
# we get letters for the groups: there are 3 different groups (a,b,c)

#add the group letters to the boxplot
boxplot(Fourtyeight~Trt, data = AN_Lipid,
        ylim = c(0,300),
        ylab="MDA (% of the control)",
        xlab="Treatments", 
          main = "Lipid peroxidation expressed as MDA concentration in Lemna minor 
        after treatments with Copper and Acer negundo extracts",
        border=c("2","3","6","7","darkgreen"))
legend(x = 0.4, y = 305, legend = c("Legend:"
                                    ,"1: Control", "2: Cu", "3: Cu+10-DOC_AN ", 
                                    "4: Cu+100-DOC_AN ", "5: 100-DOC_AN"), 
       cex = 0.8)
text( c("d","b","b","a", "c"),x=(1:5) ,y = c(130,230,230,230,140))



```
#
### **For _Acer glutinosa_ leaf extracts**


#### 1.Testing the normality of the data
```{r, fig.cap = "Figure 23. QQ plot and linear model."}

colnames(AG_Lipid)[colnames(AG_Lipid) == "48h"] <- "Fourtyeight"
# Build the linear model
model_AG_Lipid  <- lm(Fourtyeight~Trt, data = AG_Lipid)

# Create a QQ plot of residuals
qqnorm(model_AG_Lipid[["residuals"]], main = "QQ plot for model_AG_Lipid")
qqline(model_AG_Lipid[["residuals"]])
```
#

#### 2.Kruskall-Wallis groups and plot

```{r, fig.cap= "Figure 24.Lipid peroxidation expressed as MDA concentration in Lemna minor after treatments with Copper and _Acer glutinosa_ extracts."}

Krus_AG_Lipid <- agricolae::kruskal(AG_Lipid$Fourtyeight, AG_Lipid$Trt)
Krus_AG_Lipid
# we get letters for the groups: there are 4 different groups (a,b,c,d)

#add the group letters to the boxplot
boxplot(Fourtyeight~Trt, data = AG_Lipid,
        ylim = c(0,300),
        ylab="Lipid content (% of the control)",
        xlab="Treatments", 
        main = "Lipid peroxidation expressed as MDA concentration in Lemna minor 
        after treatments with Copper and Acer glutinosa extracts",
        border=c("2","3","6","7","darkgreen"))
legend(x = 0.4, y = 300, legend = c("Legend:"
                                    ,"1: Control", "2: Cu", "3: Cu+10-AG ", 
                                    "4: Cu+100-DOC_AG ", "5: 100-DOC_AG"), 
       cex = 0.8)
text( c("d","a","b","a", "c"),x=(1:5) ,y = c(130,220,160,220,140))



```
